---
title: "Regression"
output: html_notebook
---
# Introduction

This is about regression. We are going to perform regression analysis uing the marketing data of the datarium in r

# The Data

The marketing data gas 200 observations and 4 variables namely: youtube, facebook, newspaper, and sales.


```{r echo=FALSE, results='hide'}
summary(marketing$youtube)
summary(marketing$facebook)
summary(marketing$newspaper)
summary(marketing$sales)
```


# Loading Required R Packages

```{r echo=FALSE, results='hide'}
# install packages if not yet installed
library(tidyverse) # loading tidyverse 
library(caret) # loading caret
library(ggpubr) # loading ggpubr
theme_set(theme_bw()) # i don't know
```

```{r echo=FALSE, results='hide'}
# install datarium if not yet installed at the console
library(datarium) # loading datarium
```

# Preparing Data

```{r echo=FALSE, results='hide'}
# Load the data
data("marketing", package = "datarium")
# Inspect the data
sample_n(marketing, 3)
```

```{r echo=FALSE, results='hide'}
# Split the data into training and test set
set.seed(123)
training.samples <- marketing$sales %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- marketing[training.samples, ]
test.data <- marketing[-training.samples, ]
```

# Quick Start R Code

```{r echo=FALSE, results='hide'}
# Build the model
model <- lm(sales ~., data = train.data)
# Summarize the model
summary(model)
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
# (a) Prediction error, RMSE
RMSE(predictions, test.data$sales)
# (b) R-square
R2(predictions, test.data$sales)
```

```{r echo=FALSE, results='hide'}
# predicting with new data
# 
youtube <- 10
facebook <- 80
newspaper <- 0

a <- data.frame (youtube, facebook, newspaper)
p <- model %>% predict(a)
p
```

# our model is as follows:

$$\hat{y}=4.12 + 0.04x_1 + 0.21x_2 + \epsilon$$ 

where $\hat{y}$ is sales and $x_1$ is youtube, $x_2$ is facebook, and $\epsilon$ is the error term. 
